### 2015-06-12 README.Rmd
updated readme, updated vignettes, bumped patch version
ignore tests for cran push, make tnrs link not a link

	<td style="text-align:left;"><a href="http://api.phylotastic.org/tnrs">link</a></td>

@@

	<td style="text-align:left;"><a href="http://www.phylodiversity.net/phylomatic/phylomatic_api.html">link</a></td>

>>>>

	<td style="text-align:left;">"api.phylotastic.org/tnrs"</td>

@@

	<td style="text-align:left;"><a href="http://phylodiversity.net/phylomatic/html/documentation.html">link</a></td>
